---
title: "hw1"
author: "miracle ephraim"
format: pdf
editor: visual
documentclass: article
---

/newpage
# Building the Data
Answer the following based on our initial, simplified dataset of enrollments, plan types, and service areas:

/noindent 1. Provide a table of the count of plans under each plan type in each year.<br>


```{r} 
#| echo: false
#| label: tbl-plans
#| tbl-cap: All plan types in 2015
load("C:/Users/mirac/Documents/GitHub/econ470_ma/hw1/submission/hw_workspace.Rdata")
options(knitr.kable.NA = 0)
knitr::kable(plan.type.year1, 
             col.names=c("Plan Type","Count"),
             format.args=list(big.mark=","), booktabs = TRUE)
```

/noindent 2. Remove all special needs plans (SNP), employer group plans (eghp), and all "800-series" plans. Provide an updated table after making these exclusions.

```{r}
#| echo: false
#| label: tbl-plans2
#| tbl-cap: Revised plan types in 2015

options(knitr.kable.NA = 0)
knitr::kable(plan.type.year2, 
             col.names=c("Plan Type","Count"),
             format.args=list(big.mark=","), booktabs = TRUE)
``` 
/noindent 3. Provide a table of the average enrollments for each plan type in 2015.


```{r}
#| echo: false
#| label: tbl-enroll
#| tbl-cap: Enrollments by plan type in 2015

options(knitr.kable.NA = 0)
knitr::kable(plan.type.enroll, digits=0,
             col.names=c("Plan Type","Count","Avg Enrollments"),
             format.args=list(big.mark=","), booktabs = TRUE)
